---
title       : GLM's on the Swiss Data Set
subtitle    : Understanding and Explaining General Linear Models Has Become Easy
author      : Sebastian Bolz
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why Should You Know Linear Regression?

* easy to use
* easy to interpret
* applicable for a huge variety of problems
* fairly accurate

$\Rightarrow$ probably most widely used algorithm by data scientists accross the world

```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.align = 'center'}
library(ggplot2)
p <- ggplot(swiss, aes(Fertility, Infant.Mortality))
p <- p + geom_point() + stat_smooth(method = "lm")
p <- p + xlab("") + ylab("")
p
```

---

## Why Should You Know General Linear Models?

* only very few real world problems are two-dimensional
* lots of problems with discrete outcomes
* error models have to stay interpretable even when the outcome has to be positive

```{r, echo = FALSE}
glm(Infant.Mortality ~ Fertility + Education + Catholic, data = swiss)
```

---

## How Does The App Help You Understand GLM's?

---

## How Does The App Help You Explain GLM's?
